RDF Constraint Types to Ensure High Data Quality

### 2015-04-28 paper/paper7/paper7.tex
feedback

\begin{document}
\renewcommand{\arraystretch}{1.3}
%
%
%\title{RDF Validation of Metadata \\ on Person-Level and Aggregated Data}
%\title{RDF Constraints to Ensure High Quality \\ of Metadata and Data Represented by any Vocabulary }
%\title{RDF Constraints to Ensure High Quality \\ of Metadata and Data}
\title{Classification of RDF Constraint Types to Ensure High Quality of Metadata and Data}
\subtitle{}

@@

\begin{table}[H]
		\scriptsize
    \begin{center}
    \begin{tabular}{@{}lcccc@{}}
%           & \multicolumn{6}{c}{\textbf{Vocabularies}}
%    \\  \cmidrule{2-7}
    \\       \textbf{Criteria}
           & \textbf{\emph{Disco}}
           & \textbf{\emph{QB}}
					 & \textbf{\emph{SKOS}}
					 & \textbf{Total}
    \\ \midrule
		\emph{CV} & 3,575,002 (6.5\%) & 45,635,861 (83.4\%) & 5,540,988 (10.1\%) & 54,751,851 \\
		\hline
		\emph{CV (}$\mathcal{CT}_{C}$\emph{)} & 652,780 (18.3\%) & 45,634,084 (\textbf{100\%}) & 1,185,982 (21.4\%) & 47,472,846 (\textbf{86.7\%}) \\
		\emph{CV (}$\mathcal{CT}_{S}$\emph{)} & 560,857 (15.7\%) & 0 (0\%) & 4,355,006 (\textbf{78.6\%}) & 4,915,863 (9\%) \\
		\emph{CV (}$\mathcal{CT}_{B}$\emph{)} & 2,361,365 (\textbf{66.1\%}) & 1,777 (0\%) & 0 (0\%) & 2,363,142 (4.3\%) \\
		\hline
		\emph{CV (}$\mathcal{C}_B ^{\mathcal{R}}$\emph{)} & 2,333,365 (65.3\%) & 1,777 (0\%) & 0 (0\%) & 2,335,142 (4.3\%) \\
		\emph{CV (}$\overline{\mathcal{C}_B ^{\mathcal{R}}}$\emph{)} & 28,000 (0.8\%) & 0 (0\%) & 0 (0\%) & 28,000 (0.1\%) \\
		\hline
		\emph{CV ($\mathcal{SL}_{0}$)} & 1,880,777 (\textbf{52.6\%}) & 0 (0\%) & 2,281,740 (41.2\%) & 4,162,517 (7.6\%) \\
		\emph{CV ($\mathcal{SL}_{1}$)} & 1,051,757 (29.4\%) & 45,520,613 (\textbf{99,8\%}) & 3,259,248 (\textbf{58.8\%}) & 49,831,618 (\textbf{91\%}) \\
		\emph{CV ($\mathcal{SL}_{2}$)} & 642,468 (18\%) & 115,248 (0.3\%) & 0 (0\%) & 757,716 (1.4\%) \\
    \bottomrule
    \end{tabular}
    %\\ \emph{CV (constraint violations)}
    \caption{Evaluation - Constraint Violations}
		\label{tab:evaluation-constraint-violations}
    \end{center}
\end{table}

@@

>>>>

\usepackage{ntheorem}
\newtheorem{hyp}{Hypothesis}

\makeatletter
\newcounter{subhyp} 
\let\savedc@hyp\c@hyp
\newenvironment{subhyp}
 {%
  \setcounter{subhyp}{0}%
  \stepcounter{hyp}%
  \edef\saved@hyp{\thehyp}% Save the current value of hyp
  \let\c@hyp\c@subhyp     % Now hyp is subhyp
  \renewcommand{\thehyp}{\saved@hyp\alph{hyp}}%
 }
 {}
\newcommand{\normhyp}{%
  \let\c@hyp\savedc@hyp % revert to the old one
  \renewcommand\thehyp{\arabic{hyp}}%
} 
\makeatother

\usepackage{multirow}

\begin{document}
\renewcommand{\arraystretch}{1.3}
%
%
%\title{RDF Validation of Metadata \\ on Person-Level and Aggregated Data}
%\title{RDF Constraints to Ensure High Quality \\ of Metadata and Data Represented by any Vocabulary }
%\title{RDF Constraints to Ensure High Quality \\ of Metadata and Data}
\title{RDF Constraint Types to Ensure High Data Quality}
\subtitle{}

@@

\begin{table}[H]
		\scriptsize
    \begin{center}
    \begin{tabular}{@{}lcccccccc@{}}
    %       & \multicolumn{2}{c}{\textbf{Vocabularies}}
    %\\  \cmidrule{2-3}
		\hline
    \multirow{2}{*}{} &
      \multicolumn{2}{c}{\textbf{\emph{Disco}}} &
      \multicolumn{2}{c}{\textbf{\emph{QB}}} &
      \multicolumn{2}{c}{\textbf{\emph{SKOS}}} &
      \multicolumn{2}{c}{\textbf{\emph{Total}}} \\
    \textbf{} & C & CV & C & CV & C & CV & C & CV \\
    \hline
    %\\ \midrule
		 & 143 & 3,575,002 & 35 & 45,635,861 & 35 & 5,540,988 & 213 & 54,751,851 \\
		\hline
		\textbf{\emph{complex}} & 25.9\% & 18.3\% & 37.1\% & \textbf{100\%} & \textbf{37.1\%} & 21.4\% & 33.4\% & \textbf{46.6\%} \\
		\textbf{\emph{simple}} & 19.6\% & 15.7\% & 8.6\% & 0.0\% & \textbf{34.3\%} & \textbf{78.6\%} & 20.8\% & 31.4\% \\
		\textbf{\emph{vocabulary}} & \textbf{54.6\%} & \textbf{66.1\%} & \textbf{54.3\%} & 0.0\% & \textbf{28.6\%} & 0.0\% & \textbf{45.8\%} & 22.0\% \\
		%\hline
		%\emph{CV (}$\mathcal{C}_B ^{\mathcal{R}}$\emph{)} & 2,333,365 (65.3\%) & 1,777 (0\%) & 0 (0\%) & 2,335,142 (4.3\%) \\
		%\emph{CV (}$\overline{\mathcal{C}_B ^{\mathcal{R}}}$\emph{)} & 28,000 (0.8\%) & 0 (0\%) & 0 (0\%) & 28,000 (0.1\%) \\
		\hline
		\textbf{\emph{info}} & \textbf{52.5\%} & \textbf{52.6\%} & 11.4\% & 0.0\% & \textbf{60.0\%} & 41.2\% & \textbf{41.3\%} & 31.3\% \\
		\textbf{\emph{warning}} & 7.0\% & 29.4\% & 8.6\% & \textbf{99,8\%} & 14.3\% & \textbf{58.8\%} & 10.0\% & \textbf{62.7\%} \\
		\textbf{\emph{error}} & 40.6\% & 18\% & \textbf{80.0\%} & 0.3\% & 25.7\% & 0.0\% & \textbf{48.8\%} & 6.1\%\\
    \bottomrule
    \end{tabular}
    \\ \emph{C (constraints), CV (constraint violations)}
    \caption{Constraints and Constraint Violations}
		\label{tab:evaluation-constraint-violations}
    \end{center}
\end{table}

%\begin{table}[H]
		%\scriptsize
    %\begin{center}
    %\begin{tabular}{@{}lcccccccc@{}}
%%           & \multicolumn{6}{c}{\textbf{Vocabularies}}
%%    \\  \cmidrule{2-7}
    %\\       \textbf{}
           %& \textbf{\emph{Disco}}
           %& \textbf{\emph{QB}}
					 %& \textbf{\emph{SKOS}}
					 %& \textbf{Total}
					 %& \textbf{\emph{Disco}}
           %& \textbf{\emph{QB}}
					 %& \textbf{\emph{SKOS}}
					 %& \textbf{Total}
    %\\ \midrule
		 %& 3,575,002 & 45,635,861 & 5,540,988 & 54,751,851 & & & &  \\
		%\hline
		%\textbf{\emph{complex}} & 18.3\% & \textbf{100\%} & 21.4\% & \textbf{86.7\%} & & & & \\
		%\textbf{\emph{simple}} & 15.7\% & 0.0\% & \textbf{78.6\%} & 9\% & & & & \\
		%\textbf{\emph{vocabulary}} & \textbf{66.1\%} & 0.0\% & 0\% & 4.3\% & & & & \\
		%%\hline
		%%\emph{CV (}$\mathcal{C}_B ^{\mathcal{R}}$\emph{)} & 2,333,365 (65.3\%) & 1,777 (0\%) & 0 (0\%) & 2,335,142 (4.3\%) \\
		%%\emph{CV (}$\overline{\mathcal{C}_B ^{\mathcal{R}}}$\emph{)} & 28,000 (0.8\%) & 0 (0\%) & 0 (0\%) & 28,000 (0.1\%) \\
		%\hline
		%\textbf{\emph{info}} & \textbf{52.6\%} & 0.0\% & 41.2\% & 7.6\% & & & & \\
		%\textbf{\emph{warning}} & 29.4\% & \textbf{99,8\%} & \textbf{58.8\%} & \textbf{91\%} & & & & \\
		%\textbf{\emph{error}} & 18\% & 0.3\% & 0.0\% & 1.4\% & & & & \\
    %\bottomrule
    %\end{tabular}
    %%\\ \emph{CV (constraint violations)}
    %\caption{Constraint Violations}
		%\label{tab:evaluation-constraint-violations}
    %\end{center}
%\end{table}

\tb{difference between 0\% and 78.6\%}
\tb{basic constraints sind bei etablierten vokabularen publitierte datensätze werden eingehalten hohe datenqualität / schwerwiegende constraintverletzungen treten kaum auf / schwere constraints sind in idesen vielen daten nicht auf / disco ist in beiden fällen anders / erheblichen anteil von schwersten constraint verletzungen / disco neues vokabular das noch daten gelten noch einenm draft von disco oder hat disco nicht verstanden schnlechtere daten als entabliete vokabulare / es ist sinnvoll sprachen zu entwickeln komplexere constraints auszudrücken / simple und vocabulary können heute schon sehr gut beschrieben werden / wir wünschen und dass es komplexere constraint languages gibt mit denen complex constraints besser abgebildet werden können / deulticherer verbesserung in der datenualitt wenn wir diese constraint languages hätten / gibt es weitere hypothesen? - alles was in der tabelle auffällig ist / normaliisert über die datensatzgröße / 3 sehr wichtige und repräsentative vokabulare im sbe bereich / interessanate constraints mit ausreißern / hypothesen über weitere vokabulare müssen verifiziert oder falsifiziert werden / diskussion: / 3 constraints werden zufällig nie verletzt / basis für future work / motivation, dass man constraint languages entwicken muss die complexe constraints abbilden / datenqualität ist generell sehr hoch / als hypothese postulieren}

-----

\begin{hyp}

\end{hyp}

We hypothesise

-----

As the number of evaluated triples differs between the vocabularies, the stated total values are normalized percentage values.

-----

Disco is a new vocabulary which is published in 2015

for this vocabulary the published data is not consistent with the vocabulary

-----

We have to be careful making general statements for all vocabularies as we evaluate only 3 vocabularies

-----

future work:
To make general statements for all vocabularies, we will evaluate data sets of more vocabularies

-----

@@

-----

\begin{hyp}
More than the half of the vocabulary constraints are associated with the severity level error and
more than 3/4 of the simple constraints are only informational constraints. 
\end{hyp}
Table \ref{tab:evaluation-complexity-severity} shows the relation between the complexity and the severity level of all 213 constraints.

\begin{table}[H]
		\scriptsize
    \begin{center}
    \begin{tabular}{@{}lcccc@{}}
%           & \multicolumn{6}{c}{\textbf{Vocabularies}}
%    \\  \cmidrule{2-7}
    \\       \textbf{}
           & \textbf{\emph{vocabulary}}
           & \textbf{\emph{simple}}
					 & \textbf{\emph{complex}}
    \\ \midrule
		%\emph{Triples} & 9,673,055 & 3,775,983,610 & 477,737,281 & 4,263,393,946 \\
		%\emph{Data Sets} & 1,526 & 9,990 & 4,178 & 15,694 \\
		%\hline
		\textbf{\emph{info}} & 38.7 \% & \textbf{76.2 \%} & \textbf{42.3 \%} \\
		\textbf{\emph{warning}} & 6.7 \% & 7.1 \% & 13.5 \% \\
		\textbf{\emph{error}} & \textbf{54.6 \%} & 16.7 \% & \textbf{44.2 \%} \\
    \bottomrule
    \end{tabular}
    %\\ \emph{C (constraints), CT (constraint types)}
    \caption{Complexity vs. Severity of Constraints}
		\label{tab:evaluation-complexity-severity}
    \end{center}
\end{table}
